Considering scale in multilayer animal social networks

### 2020-08-17 paper/manuscript.Rmd
minor edits

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
data, the chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes at each time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment based on the chain rule
has previously been applied to caribou using a temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes and associations between
individuals in a given network layer were represented as intralayer
edges.

We weighted edges of social networks by the strength of association between
caribou using the simple ratio index [SRI, @Cairns_1987]:

@@

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou, while 500 - 1000 m represents the scale at which
caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks
consisted of the social associations between `r DT[, uniqueN(get(idcol))]`
individuals across three habitat layers (foraging, forest and open) for the
entire study period. For each land cover resolution, we calculated individual
graph strength within each habitat layer, and edge overlap and multidegree
across habitat layers.

>>>>

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
data, the chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes at each time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment based on the chain rule
has previously been applied to caribou using a temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes and associations between
individuals were represented as edges. We weighted edges by the strength of 
association between individuals using the simple ratio index [SRI, @Cairns_1987].

@@

### Spatial scale
To assess the influence of land cover spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales 
(100 - 1000 m by steps of 100 m) using a modal moving window method [@Graham_2019a]. 
We assume 30 m and 100 m represents fine-scale decision making
for caribou, while 500 - 1000 m represents the scale at which
caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks
consisted of the social associations between `r DT[, uniqueN(get(idcol))]`
individuals across three habitat layers (foraging, forest and open) for the
entire study period. For each land cover resolution, we calculated individual
graph strength within each habitat layer, and edge overlap and multidegree
across habitat layers.
